\chapter{Conclusion and Future Works}
\noindent\rule{\linewidth}{2pt}

\section{Conclusion}

This project has demonstrated a Zero-Trust security integration pattern for multi-agent AI systems by adopting the Attestix Protocol as a non-invasive middleware layer, and has identified the architectural shifts (per-agent key isolation, encrypted storage backend, multi-hop delegation) required to take the pattern from proof-of-concept to production deployment. The result is what this work terms \textbf{Regulated AI Orchestration}: AI systems where every decision is cryptographically accountable and the audit trail is suitable for review by medical, financial, legal, and environmental regulators, within the scope established in Section \ref{sec:limitations}.

Key achievements include:

\begin{itemize}
    \item \textbf{Shared Parameterised AttestixManager:} A single shared security client eliminates duplication across four domain projects, reducing domain-specific security code to a 9-line configuration file per project.

    \item \textbf{End-to-End Cryptographic Accountability:} Every AI decision is traceable from Ed25519 identity provisioning through UCAN delegation gates, W3C Verifiable Credentials, SHA-256 Merkle provenance chains, and Base L2 blockchain anchoring.

    \item \textbf{Demonstrated EU AI Act Compliance:} All agents have Annex III risk profiles, and the conformity gatekeeper actively blocks unregistered agents from execution --- confirmed through negative testing.

    \item \textbf{Framework-Agnostic Integration:} The security layer operates identically across LangChain, CrewAI, LangGraph, Semantic Kernel, and the OpenAI SDK simultaneously.

    \item \textbf{Live Blockchain Anchoring Confirmed:} A real EAS attestation (TX: \texttt{107aa293...}, UID: \texttt{0xb2cdbd85...}) on Base Sepolia confirms that audit records can be made permanently immutable and publicly verifiable.
    \item \textbf{Measured LLM Output Quality:} A 20-fixture golden-prompt evaluation harness (\texttt{evals/score\_evals.py}) with seven adversarial safety probes was executed against the regulated pipelines. The Hospital domain scored 0.890 (above the 0.80 regression bar); five of seven safety probes passed outright across all four domains.
    \item \textbf{Provider-Agnostic Inference Layer:} A single LLM factory (\texttt{shared/llm\_factory.py}) routes interchangeably to Groq \texttt{llama-3.3-70b-versatile} or AWS Bedrock \texttt{us.meta.llama3-3-70b-instruct-v1:0} with no changes to the agent code, demonstrating that the security middleware is decoupled from the LLM host.
    \item \textbf{OWASP LLM01 Boundary Mitigation:} Every external input that flows into an LLM (patient statements, ticker symbols, supplier names, contract requirements, DuckDuckGo search results, internal documents) is wrapped in spotlighting delimiters and accompanied by an injection-pattern detector. Three pytest cases regression-test the mitigation, contributing to a 13/13 overall test pass rate.
    \item \textbf{Reproducible Performance Benchmarks:} Real latency, token consumption, and on-chain gas cost numbers are published in \texttt{benchmarks/RESULTS.md} and \texttt{benchmarks/GAS\_COST.md}, replacing earlier ``appears to work'' performance claims.
\end{itemize}

\section{Future Works}

\begin{itemize}

    \item \textbf{Persistent Agent Identities and Reputation Tracking}
    \begin{itemize}
        \item Pre-provision fixed identities for individual specialist agents and reuse them across sessions.
        \item Enable the \texttt{ReputationService} to build longitudinal trust scores with 30-day exponential decay, supporting reputation-aware orchestration.
    \end{itemize}

    \item \textbf{Mainnet Blockchain Anchoring}
    \begin{itemize}
        \item Migrate blockchain anchoring from Base Sepolia testnet to Base mainnet for permanent, economically-secured proof of AI audit records.
        \item Particularly valuable for financial and legal domains where tamper-evident records must survive for years.
    \end{itemize}

    \item \textbf{HTML/PDF Compliance Report Generation}
    \begin{itemize}
        \item Integrate the Attestix \texttt{ReportService} to generate self-contained HTML/PDF compliance reports consolidating all artifacts (DIDs, VCs, audit trail, compliance profile) into a single regulator-ready document.
    \end{itemize}

    \item \textbf{Extended Adversarial Testing Framework}
    \begin{itemize}
        \item The current evaluation harness covers prompt-level safety probes (drug-allergy, hallucination, illegal-clause refusal, role-override, tool-exfiltration). Extend it to system-level adversarial cases: token forgery, proof-chain cycle injection, SSRF attacks on the DID resolver, and concurrent delegation race conditions.
    \end{itemize}

    \item \textbf{Deployment in Real Enterprise Systems}
    \begin{itemize}
        \item Deploy the architecture in a real-world multi-agent system in a regulated environment such as a hospital information system or algorithmic trading platform.
        \item Evaluate performance under production load and adapt the \texttt{ProvenanceService} for distributed, multi-node deployments.
    \end{itemize}

\end{itemize}
