\pagebreak
\phantomsection
\cleardoublepage
\addcontentsline{toc}{chapter}{Internship Certificate}

%% =====================================================================
%% Internship Certificate - VibeTensor Private Limited
%% Document ID: VT/INTC/2026/SP-2206119 (ISO 9001:2015 7.5.2)
%% Statutory letterhead per Section 12(3), Companies Act 2013:
%%   - Company name
%%   - CIN: U74909TS2025PTC197692
%%   - Registered office address
%%   - Email and website
%%   - Helpful additions: DPIIT, GSTIN
%% =====================================================================

\noindent\rule{\linewidth}{2pt}\\[0.2in]

%% --- Letterhead block ------------------------------------------------
\begin{center}
{\Large \textbf{VIBETENSOR PRIVATE LIMITED}}\\[2pt]
{\small Reg. Office: 5-11-755/2, Sagara Colony Road No.\ 2, Vidyaranyapuri,}\\
{\small Warangal, Hanamkonda, Telangana, India -- 506009}\\[2pt]
{\small CIN: U74909TS2025PTC197692 \ \ $|$ \ \ GSTIN: 36AAKCV9991Q1ZX \ \ $|$ \ \ DPIIT: DIPP206711}\\
{\small Email: info@vibetensor.com \ \ $|$ \ \ Website: www.vibetensor.com}
\end{center}

\vspace{0.15in}
\noindent\rule{\linewidth}{0.5pt}\\[0.1in]

%% --- Title ----------------------------------------------------------
\begin{center}
{\Large \textbf{\underline{INTERNSHIP CERTIFICATE}}}
\end{center}

\vspace{0.1in}

\noindent\textbf{Document ID:} VT/INTC/2026/SP-2206119 \hfill \textbf{Date of Issue:} 12 May 2026

\vspace{0.3in}

%% --- Body -----------------------------------------------------------
\noindent
\textbf{TO WHOM IT MAY CONCERN}

\vspace{0.2in}

\noindent
This is to certify that \textbf{Mr.\ Bhamidi Sai Pranay} (Roll No.\ 2206119),
a final-year student of the Bachelor of Technology programme in Computer
Science and Engineering at the National Institute of Technology Patna, was
engaged as a \textbf{Software Development Engineering Intern} at
\textbf{VibeTensor Private Limited} for the period
\textbf{05 January 2026 to 27 June 2026}.

\vspace{0.2in}

\noindent
During the internship, the candidate worked under the direct supervision of
the undersigned and contributed to the following project:

\vspace{0.1in}

\noindent
\textbf{Project:} \textit{Regulated AI Orchestration --- Integrating the
Attestix Security Protocol into Multi-Agent AI Systems.}

\vspace{0.15in}

\noindent
\textbf{Scope of work completed by the candidate:}

\begin{itemize}
\setlength\itemsep{2pt}
\item Designed and authored a shared, parameterised \texttt{AttestixManager} integration layer used uniformly across four domain pipelines.
\item Implemented four end-to-end regulated multi-agent pipelines (Healthcare, Finance, ESG Audit, Legal Advisory) using LangChain, LangGraph, CrewAI, Semantic Kernel and the OpenAI Agents SDK.
\item Engineered a provider-agnostic LLM factory enabling the same pipelines to run on either Groq llama-3.3-70b-versatile or AWS Bedrock \texttt{us.meta.llama3-3-70b-instruct-v1:0}.
\item Built an automated regression test suite (13 pytest cases, 13/13 passing) covering identity provisioning, UCAN delegation, conformity gating, Merkle chain integrity, mandatory token enforcement, and OWASP LLM01 prompt-injection mitigation.
\item Designed a golden-prompt evaluation harness (20 fixtures, 7 adversarial safety probes) and captured numeric evaluation scores against the regulated pipelines.
\item Authored an Article 10 / Article 11 / Article 43 / Annex V coverage layer aligned with the European Union Artificial Intelligence Act (Regulation (EU) 2024/1689).
\item Identified two engineering defects in the upstream Attestix library during integration testing (load-order race condition; EAS gas-limit insufficiency on Base Sepolia) and verified the corresponding upstream fixes end-to-end.
\item Anchored a regulated audit trail to the Base Sepolia Layer-2 network via the Ethereum Attestation Service, with verifiable transaction record retained as part of the project deliverables.
\end{itemize}

\vspace{0.15in}

\noindent
The above work was carried out by the candidate as part of a structured
internship engagement at VibeTensor Private Limited and is reflected in the
project report submitted in partial fulfilment of the requirements for the
award of the Bachelor of Technology degree.

\vspace{0.2in}

\noindent
\textbf{Conduct and disposition:} During the internship the candidate
demonstrated technical proficiency, intellectual honesty regarding the
boundary between his own contribution and the underlying Attestix library
(which is the intellectual property of VibeTensor Private Limited and predates
the candidate's engagement), and adherence to the company's code of conduct,
information-security policies, and data-handling guidelines.

\vspace{0.2in}

\noindent
\textbf{Intellectual property statement:} The Attestix Protocol library used
in the project is the intellectual property of VibeTensor Private Limited and
its founder, and predates the candidate's internship. The integration layer,
domain pipelines, test suite, evaluation harness, benchmarks, and report
authored by the candidate during this engagement are the contributions
recognised in this certificate, governed by the executed internship and
intellectual-property assignment agreements between VibeTensor Private
Limited and the candidate.

\vspace{0.2in}

\noindent
We wish him every success in his future academic and professional pursuits.

\vspace{0.5in}

%% --- Signature block ------------------------------------------------
\begin{flushleft}
\rule{6cm}{0.4pt}\\[0.1in]
\textbf{Mr.\ Dubasi Pavan Kumar}\\
Founder and Chief Executive Officer\\
VibeTensor Private Limited\\
Email: pavan@vibetensor.com\\[0.2in]
\textit{(Affix company seal)}
\end{flushleft}

\vfill
\noindent\rule{\linewidth}{0.5pt}\\
{\footnotesize VibeTensor Private Limited \ $|$ \ CIN U74909TS2025PTC197692 \ $|$ \ Document aligned with ISO 9001:2015 clause 7.5.2}\\
\noindent\rule{\linewidth}{2pt}
