\chapter{References}

\noindent\rule{\linewidth}{2pt}

\vspace{0.5cm}

\begin{enumerate}

\item M. Wooldridge, \textit{An Introduction to MultiAgent Systems}, 2nd ed. Chichester, UK: John Wiley \& Sons, 2009.

\vspace{0.3cm}

\item H. Chase, ``LangChain: Building applications with LLMs through composability,'' GitHub, 2023. [Online]. Available: \url{https://github.com/langchain-ai/langchain}

\vspace{0.3cm}

\item J. Moura, ``CrewAI: Framework for orchestrating role-playing, autonomous AI agents,'' GitHub, 2024. [Online]. Available: \url{https://github.com/crewAIInc/crewAI}

\vspace{0.3cm}

\item Microsoft, ``Semantic Kernel,'' GitHub, 2024. [Online]. Available: \url{https://github.com/microsoft/semantic-kernel}

\vspace{0.3cm}

\item F. Perez and I. Ribeiro, ``Ignore previous prompt: Attack techniques for language models,'' \textit{arXiv:2211.09527}, 2022.

\vspace{0.3cm}

\item J. H. Saltzer and M. D. Schroeder, ``The protection of information in computer systems,'' \textit{Proc. IEEE}, vol. 63, no. 9, pp. 1278--1308, 1975.

\vspace{0.3cm}

\item European Parliament, ``Regulation (EU) 2024/1689 on Artificial Intelligence,'' \textit{Official Journal of the European Union}, June 2024.

\vspace{0.3cm}

\item M. Sporny et al., ``Decentralized Identifiers (DIDs) v1.0,'' W3C Recommendation, July 2022. [Online]. Available: \url{https://www.w3.org/TR/did-core/}

\vspace{0.3cm}

\item M. Sporny et al., ``Verifiable Credentials Data Model v1.1,'' W3C Recommendation, March 2022. [Online]. Available: \url{https://www.w3.org/TR/vc-data-model/}

\vspace{0.3cm}

\item B. Zelenka et al., ``UCAN Specification v0.9,'' UCAN Working Group, 2022. [Online]. Available: \url{https://github.com/ucan-wg/spec}

\vspace{0.3cm}

\item M. S. Miller, K.-P. Yee, and J. S. Shapiro, ``Capability myths demolished,'' Technical Report SRL2003-02, Johns Hopkins University, 2003.

\vspace{0.3cm}

\item B. Laurie, A. Langley, and E. Kasper, ``Certificate Transparency,'' RFC 6962, IETF, June 2013.

\vspace{0.3cm}

\item Ethereum Attestation Service, ``EAS: A public good for making attestations,'' 2023. [Online]. Available: \url{https://attest.org}

\vspace{0.3cm}

\item Coinbase, ``Base: An Ethereum L2 Built on the OP Stack,'' 2024. [Online]. Available: \url{https://base.org}

\vspace{0.3cm}

\item P. K. Dubasi, ``Attestix: A Unified Attestation Infrastructure for Autonomous AI Agents,'' VibeTensor Technical Report, 2026. Source: \url{https://github.com/VibeTensor/attestix/blob/main/paper/attestix-paper.tex}. Compiled documentation: \url{https://attestix.io/docs/research}.

\vspace{0.3cm}

\item P. K. Dubasi, ``Attestix v0.3.0,'' Python Package Index (PyPI), 2026. [Online]. Available: \url{https://pypi.org/project/attestix/}

\vspace{0.3cm}

\item Groq Inc., ``Groq API,'' 2024. [Online]. Available: \url{https://groq.com}

\end{enumerate}
